Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-25 paper/authors.tex
update paper
minor manuscript updates

%
% key authors:
%

@@

%PENDING
\author[0000-0002-9158-7315]{R. Brahm}
\affiliation{Center of Astro-Engineering UC, Pontificia Universidad
Cat\'olica de Chile, Av. Vicu\~na Mackenna 4860, 782-0436 Macul,
Santiago, Chile}
\affiliation{Instituto de Astrof\'isica, Facultad de F\'isica,
Pontificia Universidad Cat\'olica de Chile, Av. Vicu\~na Mackenna
4860, 782-0436 Macul, Santiago, Chile}
\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
Mackenna 4860, 782-0436 Macul, Santiago, Chile}

@@

@@

%
% SG1 contributors: ask Karen -- are there others?
%
%PENDING
\author{P. Evans}
\affiliation{El Sauce Observatory, Coquimbo Province, Chile}

@@

%
% SG2 contributors
%
%PENDING
\author[0000-0002-4891-3517]{G. Zhou}
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

@@

@@

% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%CONFIRMED
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%CONFIRMED
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%PENDING
\author{S. Seager} % seager@mit.edu
\affiliation{Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

>>>>

%
% key contributions
%

@@

\author[0000-0002-9158-7315]{R. Brahm}
\affiliation{Center of Astro-Engineering UC, Pontificia Universidad
Cat\'olica de Chile, Av. Vicu\~na Mackenna 4860, 782-0436 Macul,
Santiago, Chile}
\affiliation{Instituto de Astrof\'isica, Facultad de F\'isica,
Pontificia Universidad Cat\'olica de Chile, Av. Vicu\~na Mackenna
4860, 782-0436 Macul, Santiago, Chile}
\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
Mackenna 4860, 782-0436 Macul, Santiago, Chile}

@@

%PENDING
\author{P. Evans}
\affiliation{El Sauce Observatory, Coquimbo Province, Chile}

%PENDING
\author[0000-0002-4891-3517]{G. Zhou}
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

@@

%PENDING
\author[0000-0003-2989-7774]{C. Bergmann}
\affilation{Exoplanetary Science at UNSW, School of Physics, UNSW
Sydney, NSW 2052, Australia}

%PENDING
\author[0000-0002-3481-9052]{K. G. Stassun}
\affiliation{Vanderbilt University, Department of Physics \& Astronomy,
6301 Stevenson Center Lane, Nashville, TN 37235, USA}
\affiliation{Fisk University, Department of Physics, 1000 17th Avenue
N., Nashville, TN 37208, USA}
%

%
% SG1 contributors: ask Karen -- are there others?
%

@@

%
% SG2 contributors
%

@@

%PENDING
\author[0000-0002-7595-0970]{C.~.G.~Tinney}
\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
Sydney, NSW 2052, Australia}
\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW
2052, Australia}

@@

% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%PENDING
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%PENDING
\author{S. Seager} % seager@mit.edu
\affiliation{Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

### 2020-05-25 paper/ms.tex
minor manuscript updates

\begin{abstract}
We report the discovery of the transiting planet TOI 837.01,
a warm Jupiter-sized planet ($R_{\rm p} = 10.XX\,R_\oplus$, $P =
8.YY\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$.
TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602 (the
``Southern Pleiades'') and is therefore 50 million years old.
We characterize the system using data from the NASA {\it Transiting
Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
XXX/FEROS, and AAT/Veloce.
TOI 837.01 joins the growing ranks of adolescent exoplanets orbiting
bright host stars, and is amenable for studies of planetary
atmospheric and orbital evolution.
\end{abstract}

@@

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
  \texttt{IPython} \citep{perez_2007},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}

>>>>

\begin{abstract}
We report the validation of the transiting planet TOI 837.01,
a warm Jupiter-sized planet ($R_{\rm p} = 10.XX\,R_\oplus$, $P =
8.3Y\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$ (3$\sigma$).
TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602 (the
``Southern Pleiades''). It is therefore 50 million years old.
We characterize the system using data from the NASA {\it Transiting
Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
XXX/FEROS, and AAT/Veloce.
TOI 837.01 joins the growing ranks of adolescent exoplanets orbiting
bright host stars, and is amenable for studies of planetary
atmospheric and orbital evolution.
\end{abstract}

@@

"""Validation is the process of statistically arguing that a
transit-like signal is due to a planet rather than an astrophysical
false positive. """
(CITE blender, Torres+04,05,10; vespa Morton 12, 15; pastis Diaz+14
Santerne+15; triceratops Giacalone \& Dressing 20).
In this study, we provide such statistical arguments.

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
  \texttt{IPython} \citep{perez_2007},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
